Sampling deaths and OLS

### 2018-01-21 ols.Rmd
change

We check the effect of assuming normally distributed remaining life after age 60.

@@

# Standard survival analyses

>>>>

We check the effect of studying mortality of the dead and whether it is reasonable to assume normally distributed remaining life after age 60.

@@

# Survival analysis with OLS

## Full data

*OLS* means assuming *normally distributed* remaining life after 60, and we can use standard linear regression. In the case of right censoring, we need to fall back on maximum likelihood for the estimation. The function *survreg* in the **R** package **survival** facilitates this.

```{r survrcens}
fit <- survreg(Surv(exit, event) ~ sex + region, data = ols, dist = "gaussian")
x <- summary(fit)
x
```

So the *e60* for men from Skellefteå is `r round(x$coef[1], 2)` and for women it is `r round(x$coef[2], 2)` more years.
